Response to the defense feedback

### 2021-05-30 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Multiple Leakages Sites}
Real-world software can have many side-channel vulnerabilities. These vulnerabilities may spread throughout the whole program. An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}. In order to precisely quantify the
total information leakage, we need to know the relation of these leakage sites.

@@

Suppose one program has two side-channel vulnerabilities A and B, which can leak $L_A$ and $L_B$ bits respectively, according to the definition~\ref{chapter5:def}. 
Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:

>>>>

\section{Multiple Leakages Sites}
Real-world software can have many side-channel vulnerabilities. These vulnerabilities may spread throughout the whole program. An adversary may exploit more than one side-channel vulnerabilities to gain more information~\cite{7163052, 191010}. In order to quantify the
total information leakage precisely, we need to know the relation of these leakage sites.

@@

Suppose one program has two side-channel vulnerabilities $A$ and $B$, which can leak $L_A$ and $L_B$ bits, respectively, according to Definition~\ref{chapter5:def}. 
Depending on the relation between A and B, the total leaked information $L_{\mathit{total}}$ will be:
